---
title: "ECON 344 Final"
output: 
  html_document:
    toc: true
    theme: united
    includes:
      after_body: footer.html
author: "Brice Wilbanks"
runtime: shiny
---
```{r, echo=FALSE, include = FALSE}
library(car)
library(dynlm)
library(knitr)
library(stargazer)
require(ggplot2)
require(ggiraph)
require(ggiraphExtra)
require(plyr)
require(Epi)
skiraw <- read.csv("SkiData_Raw.csv", 
                   sep = ',',
                   stringsAsFactors = FALSE
                   )
timeseries<-ts(skiraw, start=c(1990,1))
cormatrix <- cor(timeseries)
#stargazer(cormatrix, title="Correlation Matrix", type="html")
```
# Plotting the Variables

Below are plots for each of the used independent variables (x-axis) against the chosen dependent variable of annual skier visits per acre (y-axis). The interactive tool below allows readers to choose an independent variable of their choice. 

```{r echo = FALSE}
#stat.table(index=X,contents = mean(), data=skiraw, margins = FALSE)
selectInput("ind_var", "Variable:",
 c(
   "Retail Sales Tax Collected"="Retail.Sales.Tax.Collected..Inflation.","Total Retail Sales"="Total.Retail.Sales..Inflation.","Retail Square Footage (Breckenridge)"="Retail.Square.Footage","Unemployment Rate (Summit County)"="Unemployment.Rate..Summit.","CPI (Nation)"="CPI","Total Nearby Housing"="Total.Nearby.Housing","Annual Median Income (Summit County)"="Annual.Income..Summit.","Annual Median Income (Colorado)"="Annual.Income..Colorado.","Green Terrain Percentage"="Skiable.Green.Terrain","Blue Terrain Percentage"="Skiable.Blue.Terrain","Black Terrain Percentage"="Skiable.Black.Terrain","Double Black Terrain Percentage"="Skiable.Double.Black.Terrain","Snowmaking Acres"="Snowmaking.Acres","Breckenridge Permanent Residents"="Breckenridge.Permanent.Residents","Breckenridge Peak Residents"="Breckenridge.Peak.Residents","Upper Blue Permanent Residents"="Upper.Blue.Permanent.Residents","Upper Blue Peak Residents"="Upper.Blue.Peak.Residents","Summit County Permanent Residents"="Summit.County.Permanent.Residents","Summit County Peak Residents"="Summit.County.Peak.Residents")) 
```
```{r echo = FALSE}
renderPlot({
ggplot(data = skiraw, aes_string(x = input$ind_var, y = "Visitors.by.Acres"))+
  geom_point()
})

```


# Model 1 - The Economy on Skiing

### Model1_a
In this model, all macroeconic factors in Summit County are considered.

```{r, results='asis'}
model1_a <- dynlm(Visitors.by.Acres~
                  lag(Visitors.by.Acres,1)+
                  CPI+
                  Annual.Income..Summit.+
                  Unemployment.Rate..Summit.
                  ,
             data=timeseries)

model1_a_resid <- resid(model1_a)
model1_a_resid_squared <- model1_a_resid^2
model1_a_yhat <- predict(model1_a)
head(model1_a_yhat)
model1_a_yhat_squared <- model1_a_yhat^2
model1_a_hetero <- lm(
                    model1_a_resid_squared~
                    #lag(Visitors.by.Acres,1)+
                    #CPI+
                    #Annual.Income..Summit.+
                    #Unemployment.Rate..Summit.+
                    model1_a_yhat+
                    model1_a_yhat_squared)

suppressWarnings(
  stargazer(
    model1_a,
    #model1_a_hetero,
    dep.var.labels = c("",""),
    column.labels = c("Model1 A", "Heteroskedastic Test"),
    covariate.labels = c("Visitors per Acre Lagged 1 Year", "CPI", "Annual Income (Summit County)" ,"Unemployment"),
    colnames = FALSE,
    model.numbers = FALSE,
    type = "html",
    title = "Model&nbsp;1A&nbsp;Summary",
    align=TRUE,
    notes.align = "l",
    no.space=TRUE,
    report=('vc*p')
  )
)
```

<br>

### Model1_b
In this model, monetary factors of Colorado are analzed with a one year lag. Median annual income is for the state at large.
```{r, results='asis'}
model1_b <- dynlm(Visitors.by.Acres~
                  lag(Visitors.by.Acres,1)+
                  CPI+
                  Annual.Income..Colorado.
                  ,
             data=timeseries)

suppressWarnings(
  stargazer(
    model1_b,
    dep.var.labels = c(""),
    column.labels = c("Model 1B"),
    covariate.labels = c("Visitors per Acre Lagged 1 Year", "CPI", "Annual Income (Colorado)", "Intercept"),
    colnames = FALSE,
    model.numbers = FALSE,
    type = "html",
    title = "Model&nbsp;1B&nbsp;Summary",
    align=TRUE,
    notes.align = "l",
    no.space=TRUE,
    report=('vc*p')
  )
)
```


### Model1_c
In this model, the monetary factors of CPI and annual income in Summit County are analyzed with a 1 year lag.
```{r, results='asis'}
model1_c <- dynlm(Visitors.by.Acres~
                  lag(Visitors.by.Acres,1)+
                  CPI+
                  Annual.Income..Summit.
                  ,
             data=timeseries)

suppressWarnings(
  stargazer(
    model1_c,
    dep.var.labels = c(""),
    column.labels = c("Model 1C"),
    covariate.labels = c("Visitors per Acre Lagged 1 Year", "CPI", "Annual Income (Summit County)", "Constant"),
    colnames = FALSE,
    model.numbers = FALSE,
    type = "html",
    title = "Model&nbsp;1C&nbsp;Summary",
    align=TRUE,
    notes.align = "l",
    no.space=TRUE,
    report=('vc*p')
  )
)
```

<br><br>
Jump To...<br>
[Model1_d](#model1_d) CPI and Annual Income w/o Lag<br>
[Model1_e](#model1_e) Unemployment<br>
[Model1_f](#model1_f) CPI & Homoscedasticity<br>
[Model1_g](#model1_g) Annual Income & Homoscedasticity<br>
[Plot Maker](#plot-maker) Plot Models

### Model1_d <a name="model1_d"></a> 
In this model, real-time CPI and annual income are analyzed with no lag.

```{r, results='asis'}
model1_d <- dynlm(Visitors.by.Acres~
                  CPI+
                  Annual.Income..Colorado.
                  ,
             data=timeseries)
suppressWarnings(
  stargazer(
    model1_d,
    dep.var.labels = c(""),
    column.labels = c("Model 1D"),
    covariate.labels = c("CPI", "Annual Income", "Intercept"),
    colnames = FALSE,
    model.numbers = FALSE,
    type = "html",
    title = "Model&nbsp;1D&nbsp;Summary",
    align=TRUE,
    notes.align = "l",
    no.space=TRUE,
    report=('vc*p')
  )
)
```
<br>
Against the earlier hypothesis for model1_c, we see that even without a lag, CPI and Annual Income are not related to skier visits per acre. We will stop testing this branch of the model and instead focus on isolating some of the economic incicators.
<br>[Plot This!](#plot-maker)

### Model1_e <a name="model1_e"></a>
In this model, unemployment is isolated with no lag.
```{r, results='asis'}
model1_e <- dynlm(Visitors.by.Acres~
                  Unemployment.Rate..Summit.
                  ,
             data=timeseries)
suppressWarnings(
  stargazer(
    model1_e,
    dep.var.labels = c(""),
    column.labels = c("Model 1E"),
    covariate.labels = c("Unemployment", "Intercept"),
    colnames = FALSE,
    model.numbers = FALSE,
    type = "html",
    title = "Model&nbsp;1E&nbsp;Summary",
    align=TRUE,
    notes.align = "l",
    no.space=TRUE,
    report=('vc*p')
  )
)

```
<br>
In model1_d, we can see unemployment alone is not significantly correlated to skier visits.
<br>[Plot This!](#plot-maker)<br>

### Model1_f <a name="model1_f"></a>
In this model, we look at national CPI.
```{r, results='asis'}
model1_f <- dynlm(Visitors.by.Acres~
                  CPI
                  ,
             data=timeseries)
suppressWarnings(
  stargazer(
    model1_f,
    dep.var.labels = c(""),
    column.labels = c("Model 1F"),
    covariate.labels = c("CPI", "Intercept"),
    colnames = FALSE,
    model.numbers = FALSE,
    type = "html",
    title = "Model&nbsp;1F&nbsp;Summary",
    align=TRUE,
    notes.align = "l",
    no.space=TRUE,
    report=('vc*p')
  )
)
```
<br>
In model1_e, we find that CPI is significant in relation to skier visits per acre. We will also test to ensure homoscedasticity since our p-value is potentially significant. 
<br>[Plot This!](#plot-maker)
```{r, results='asis'}
model1_f_resid <- resid(model1_f)
model1_f_resid_squared <- model1_f_resid^2
model1_f_yhat <- predict(model1_f)
model1_f_yhat_squared <- model1_f_yhat^2
model1_f_hetero <- lm(model1_f_resid_squared~
                        CPI+
                        model1_f_yhat+
                        model1_f_yhat_squared
                        ,
                      data=timeseries
                      )

suppressWarnings(
  stargazer(
    model1_f,
    model1_f_hetero,
    dep.var.labels = c("",""),
    column.labels = c("Model 1F", "Heteroskedastic Test"),
    covariate.labels = c("CPI" , "ŷ","ŷ ^ 2", "Intercept"),
    colnames = FALSE,
    model.numbers = FALSE,
    type = "html",
    title = "Model&nbsp;1F&nbsp;Summary",
    align=TRUE,
    notes.align = "l",
    no.space=TRUE,
    report=('vc*p')
  )
)
```
<br>

### Model1_g <a name="model1_g"></a>
In this model, we look at just annual income in Summit County.
```{r, results='asis'}
model1_g <- dynlm(Visitors.by.Acres~
                  Annual.Income..Summit.,
                  data=timeseries)
suppressWarnings(
  stargazer(
    model1_g,
    dep.var.labels = c(""),
    column.labels = c("Model 1G"),
    covariate.labels = c("Annual Income (Summit)", "Intercept"),
    colnames = FALSE,
    model.numbers = FALSE,
    type = "html",
    title = "Model&nbsp;1G&nbsp;Summary",
    align=TRUE,
    notes.align = "l",
    no.space=TRUE,
    report=('vc*p')
  )
)
```
<br>

```{r, results='asis'}
model1_g_resid <- resid(model1_g)
model1_g_resid_squared <- model1_g_resid^2
model1_g_yhat <- predict(model1_g)
model1_g_yhat_squared <- model1_g_yhat^2
model1_g_hetero <- lm(model1_g_resid_squared~
                        Annual.Income..Summit.+
                        model1_g_yhat+
                        model1_g_yhat_squared,
                      data=timeseries,
                      na.action=na.omit
                      )
suppressWarnings(
  stargazer(
    model1_g,
    model1_g_hetero,
    dep.var.labels = c("",""),
    column.labels = c("Model1 G", "Heteroskedastic Test"),
    covariate.labels = c("Annual Income (Summit)" , "ŷ","ŷ ^ 2", "Intercept"),
    colnames = FALSE,
    model.numbers = FALSE,
    type = "html",
    title = "Model1G&nbsp;Summary",
    align=TRUE,
    notes.align = "l",
    no.space=TRUE,
    report=('vc*p')
  )
)
```
<br>[Plot This!](#plot-maker)


# Model 2 - Skiable Terrain Offered
In this model, we will be looking at the terrain offered at Breckenridge Ski Resort. During this test, we will also be testing for heteroscedasticity. We will not be lagging the year on this model as skiers pick resorts at real-time for terrain reasons. More on this in the paper.
```{r, results='asis'}
model2_a <- dynlm(Visitors.by.Acres~
                    Skiable.Green.Terrain+
                    Snowmaking.Acres
                  ,
             data=timeseries)

model2_a_resid <- resid(model2_a)
model2_a_resid_squared <- model2_a_resid^2
model2_a_yhat <- predict(model2_a)
model2_a_yhat_squared <- model2_a_yhat^2
model2_a_hetero <- lm(model2_a_resid_squared~
                        Skiable.Green.Terrain+
                        Snowmaking.Acres+
                        model2_a_yhat+
                        model2_a_yhat_squared,
                      data=timeseries
                      )

suppressWarnings(
  stargazer(
    model2_a,
    model2_a_hetero,
    dep.var.labels = c("",""),
    column.labels = c("Model 2A", "Heteroskedastic Test"),
    covariate.labels = c("Green Terrain Percent", "Snowmaking Acres", "ŷ","ŷ ^ 2", "Intercept"),
    colnames = FALSE,
    model.numbers = FALSE,
    type = "html",
    title = "Model&nbsp;2A&nbsp;Summary",
    align=TRUE,
    notes.align = "l",
    no.space=TRUE,
    report=('vc*p')
  )
)
```
<br>[Plot This!](#plot-maker)

# Plot Maker
```{r echo = FALSE}
selectInput("user_model", "Model:",
 c(
   "model1_a",
   "model1_b",
   "model1_c",
   "model1_d",
   "model1_e",
   "model1_f",
   "model1_g",
   "model2_a"
   )
 )

```
```{r echo = FALSE}
renderUI({
  selectInput("user_x", "Variable:",
    names(get(input$user_model)$coefficients[-1])
  )
})
```
```{r echo = FALSE}
renderPlot({
ggplot(get(input$user_model), aes_string(x = input$user_x, y = "Visitors.by.Acres")) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red")
})
```

